 

### 2023-06-27 markdown/discussion.Rmd
minor bugfix

#optimal_clusters <- 4

@@

ggplot(dimred_pca, aes(x=PC1, 
                       y=PC2,
                       shape = SampleType,
                       color=cluster)) +
  geom_point() +
  guides(color="none", shape="none") +
  labs(title=paste("Principle Components with", optimal_clusters, "clusters")) +
  stat_ellipse(data = dimred_pca, 
               aes(fill = cluster),
               geom = "polygon", 
               alpha = 0.2, 
               level = 0.9, 
               type = "norm", 
               linetype = 2, 
               show.legend = F,
               na.rm = T) +
  coord_fixed()

# ggplot(dimred_pca, aes(x=PC1, 
#                        y=PC2,
#                        shape = SampleType
#                        )) +
#   geom_mark_ellipse(aes(fill=cluster, color=cluster)) +
#   geom_point()
```

>>>>

#optimal_clusters <- 2

@@

ggplot(dimred_pca, aes(x=PC1, 
                       y=PC2,
                       shape = SampleType,
                       color=cluster)) +
  geom_point() +
#  guides(color="none", shape="none") +
  labs(title=paste("Principle Components with", optimal_clusters, "clusters")) +
  # stat_ellipse(data = dimred_pca, 
  #              aes(fill = cluster),
  #              geom = "polygon", 
  #              alpha = 0.2, 
  #              level = 0.9, 
  #              type = "norm", 
  #              linetype = 2, 
  #              show.legend = F,
  #              na.rm = T) +
  coord_fixed()
```
